SDR enhancement by clouds

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 12:14

```{r CEmeanDaily, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
knitr::include_graphics("../images/daily-12.png")
```

>>>>

```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean trend of CE over irradiance."}
knitr::include_graphics("../images/P_daily_trend-1.png")
```

# ```{r CEmeanDaily2, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
# knitr::include_graphics("../images/daily-12.png")
# ```
